The \tsc{r}-pronoun and postposition \tit{waar-mee} in Dutch

### 2020-01-20 paper.tex
comments on bulgarian
maybe not that different after all

\ex.\label{ex:bulgarian}
\ag. Tazi duma m -i e nepoznata.\\
that word I -\tsc{dat} is unfamiliar\\
`That word is unfamiliar to me.'\label{ex:bulpron}
\bg. Tazi duma e nepoznata na sina mi.\\
that word is unfamiliar to son my\\
`That word is unfamiliar to my son.'\label{ex:buldpto} \hfill (Bulgarian, \citealt[39]{caha2009})

@@

\ex.
\ag. Ik schilder 'r -mee.\\
 I paint there -with\\
 `I am painting with it.'\label{ex:dutchina}
\bg. *Ik schilder met 't\\
 I paint with it\\
 `I am painting with it.'\label{ex:dutchinmet}

>>>>

%%no complementary distribution in Bulgarian! So different! Nelli =b-example

\ex.\label{ex:bulgarian}
\ag. Tazi duma m -i e nepoznata.\\
that word I -\tsc{acc/dat.cl} is unfamiliar\\
`That word is unfamiliar to me.'\label{ex:bulpron}
\bg. Tazi duma e nepoznata na m -en.\\
that word is unfamiliar to me -\tsc{acc/dat.full}\\
`That word is unfamiliar to me. (with contrast)'
\bg. Tazi duma e nepoznata na sina mi.\\
that word is unfamiliar to son my\\
`That word is unfamiliar to my son.'\label{ex:buldpto} \hfill (Bulgarian, \citealt[39]{caha2009})

@@

%%Maybe save the day: in Dutch you can also use \tit{dat} in that position. So here is another difference between Bulgarian and Dutch: not with clitics, but with weak pronouns

\ex.
\ag. Ik schilder 'r -mee.\\
 I paint there -with\\
 `I am painting with it.'\label{ex:dutchina}
\bg. *Ik schilder met 't.\\
 I paint with it\\
 `I am painting with it.'\label{ex:dutchinmet}
\bg. Ik schilder met dat.\\
 I paint with that\\
 `I am painting with it.'
